---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/widgetcard.svg?branch=master)](https://travis-ci.org/hrbrmstr/widgetcard) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/widgetcard/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/widgetcard)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/widgetcard)](https://cran.r-project.org/package=widgetcard)

# widgetcard

Tools to Enable Easier Content Embedding in Tweets

## Description

Tools to Enable Easier Content Embedding in Tweets

## What's Inside The Tin

The following functions are implemented:

- `card_widget`:	Turn an htmlwidget into a web deployable, interactive Twitter card
- `gg_preview`:	Generate a Twitter Player card preview image from a ggplot2 plot

## Installation

```{r install-ex, eval=FALSE}
install.packages("widgetcard", repos = "https://cinc.rud.is/")
# or
devtools::install_git("https://git.sr.ht/~hrbrmstr/widgetcard")
# or 
devtools::install_gitlab("hrbrmstr/widgetcard")
# or (if you must)
devtools::install_github("hrbrmstr/widgetcard")
```

## Usage

See [the vignette](https://rud.is/dl/creating-interactive-player-cards.html).

## widgetcard Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
